Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
No definitions in abstract

  So far, the best known lower bound for the competitive ratio of
	deterministic algorithms was $\Omega(k)$,
 by reduction from online paging.
  We improve this result significantly by providing the lower bound of $\Omega(k\cdot \ell)$.
  We follow up with an optimal algorithm for $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partitioning (a.k.a~a \emph{configuration})
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

The online \emph{balanced repartitioning} problem (\OBRP{}) is defined as
follows. We are given a set of $n$ nodes,
initially arbitrarily partitioned into $\ell$~clusters,
each of size~$k$.
The input consists of a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a fixed amount of data.
Nodes in $C \subset V$ are \emph{collocated}
if they reside in the same cluster.
An algorithm serves a communication request between two nodes
either \emph{locally} at cost~0
if they are collocated,
or \emph{remotely} at cost~1
if they are located in different clusters.
We refer to the two types of requests as \emph{internal}
and \emph{external} requests, respectively.
Before serving a request,
an online algorithm may \emph{repartition},
%(i.e., \emph{reconfigure}).
i.e.,
it may (optionally) move some nodes into clusters different than their current clusters while respecting the capacity of every cluster. 
Only after a repartitioning is completed,
the algorithm serves the  request.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $\ALG$,
its cost,
denoted by $\ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $\ALG$ while serving the sequence $\sigma$.
The objective is to minimize the total incurred cost.

@@

\todo{ACM format for review? Is there any specific format like this? With line numbers etc.}

>>>>

  So far, the best known lower bound for the competitive ratio of
	deterministic algorithms was $\Omega(k)$,
 by reduction from online paging.
  We improve this result significantly by providing the lower bound of $\Omega(k\cdot \ell)$.
  We follow up with an optimal algorithm for $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal strategy is to move to a fixed configuration
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

The online \emph{balanced repartitioning} problem (\OBRP{}) is defined as
follows. We are given a set of $n$ nodes,
initially arbitrarily partitioned into $\ell$~clusters,
each of size~$k$.
The input consists of a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a fixed amount of data.
Nodes in $C \subset V$ are \emph{collocated}
if they reside in the same cluster.
An algorithm serves a communication request between two nodes
either \emph{locally} at cost~0
if they are collocated,
or \emph{remotely} at cost~1
if they are located in different clusters.
We refer to these two types of requests as \emph{internal}
and \emph{external} requests, respectively.
Before serving a request,
an online algorithm may \emph{repartition},
%(i.e., \emph{reconfigure}).
i.e.,
it may (optionally) move some nodes into clusters different than their current clusters while respecting the capacity of every cluster. 
Only after a repartitioning is completed,
the algorithm serves the  request.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $\ALG$,
its cost,
denoted by $\ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $\ALG$ while serving the sequence $\sigma$.
The objective is to minimize the total incurred cost.

@@

\todo{ACM format for review? Is there any specific format like this? Author anonymous, with line numbers etc.}
